### 2016-05-31 paper/fig_dnf-regex-syntax.tex
added in some clenaer stuff

% DNF_REGEX
(Atoms)& \Atom{} & \GEq{} & \RegexVariable{} & variable\\
& & &\GBar{} \DNFRegex{}* & iterate \\
(Conjunct)& \Conjunct{} & \GEq{} &
$[\String_0;\Atom_1;\ldots;\Atom_n;\String_n]$ & conjunct\\
(DNF Regex)& \DNFRegex{} & \GEq{} & $[\Conjunct_1;\ldots;\Conjunct_n]$ & dnf regex\\
\end{tabular}
\caption{DNF Regex Syntax}
\label{fig:dnf-regex-syntax}
\end{figure}

>>>>

% DNF_REGEX
(Atoms)& \Atom{},\AtomAlt{} & \GEq{} & \DNFRegex{}* & Iterate DNF\\
(Conjunct)& \Conjunct{},\ConjunctAlt{} & \GEq{} &
$[\String_0;\Atom_1;\ldots;\Atom_n;\String_n]$ & Conjoin\\
(DNF Regex)& \DNFRegex{},\DNFRegexAlt{} & \GEq{} & $[\Conjunct_1;\ldots;\Conjunct_n]$ & DNF Or\\
\end{tabular}
\caption{DNF Regex Syntax}
\label{fig:dnf-regex-syntax}
\end{figure}

### 2016-05-31 paper/fig_regex-syntax.tex
added in some clenaer stuff

% REGEX
(Regexs)& \Regex{} & \GEq{} & \RegexVariable{} & variable \\
& & & \GBar{} s $\in \Sigma^*$ & base \\
& & & \GBar{} \Regex{}* & star \\
& & & \GBar{} $\Regex_1 \Regex_2$ & concat \\
& & & \GBar{} $\Regex_1 | \Regex_2$ & or \\
\end{tabular}
\caption{Regex Syntax}
\label{fig:regex-syntax}
\end{figure}

>>>>

% REGEX
(String)& \String{},\StringAlt{} & \GEq{} & $\String\in\Star{\Sigma}$ \\
(Regexs)& \Regex{},\RegexAlt{} & \GEq{} & s & Base \\
& & & \GBar{} \Regex{}* & Star \\
& & & \GBar{} $\RegexConcat{\Regex_1}{\Regex_2}$ & Concat \\
& & & \GBar{} $\Regex_1 | \Regex_2$ & Or \\
\end{tabular}
\caption{Regex Syntax}
\label{fig:regex-syntax}
\end{figure}
